### 2015-07-28 doc/manual/runs.tex
Bugfix in radialScans

The magnetic drift terms introduce nonzeros in the system matrix,
and therefore increase the memory required for factorization; a typical increase is 30-40\%.
These magnetic drift terms often have only a minor effect, except perhaps when the radial
electric field is near 0.

If the electrostatic potential is not constant on flux surfaces and poloidal/toroidal magnetic drifts
are included, certain terms exist in the kinetic equation which have not yet been implemented in the code.
Thus, at present it is not strictly correct to simultaneously set  \parlink{magneticDriftScheme} > 0 
and  \parlink{includePhi1} = \true.

>>>>

The magnetic drift terms introduce nonzeros in the system matrix,
and therefore increase the memory required for factorization; a typical increase is 20-40\%.
These magnetic drift terms typically have a minor effect except when the radial
electric field is near 0.

If the electrostatic potential is not constant on flux surfaces and poloidal/toroidal magnetic drifts
are included, certain terms exist in the kinetic equation which have not yet been implemented in the code.
Thus, at present it is not strictly correct to simultaneously set  \parlink{magneticDriftScheme} $> 0$ 
and  \parlink{includePhi1} = \true.
